Towards human SuperEEG

### 2018-10-09 paper/main.tex
swapped in newer figures for main text; supp figures still in progress
checking in remaining edits from meeting with lucy

\newcommand{\taskrecon}{S1}
\newcommand{\perexpcorrmaps}{S2}
\newcommand{\perexptaskrecon}{S3}
\newcommand{\perexptaskreconseparated}{S4}
\newcommand{\suppstats}{S5}

@@

The recording from a given electrode is maximally informative about
the activity of the neural tissue immediately surrounding its
recording surface.  However, brain regions that are distant from the
recording surface of the electrode also contribute to the recording,
albeit (ceteris paribus) to a much lesser extent.  One mechanism
underlying these contributions is volume conduction.  The precise rate
of falloff due to volume conduction (i.e., how much a small volume of
brain tissue at location $x$ contributes to the recording from an
electrode at location $\eta$) depends on the size of the recording
surface, the electrode's impedance, and the conductance profile of the
volume of brain between $x$ and $\eta$.  As an approximation of this
intuition, we place a Gaussian radial basis function (RBF) at the
location $\eta$ of each electrode's recording surface
(Fig.~\ref{fig:methods}B).  We use the values of the RBF at any brain
location $x$ as a rough estimate of how much structures around $x$
contributed to the recording from location $\eta$:
\begin{align}
  \mathrm{rbf}(x|\eta,\lambda) & =
  \mathrm{exp}\left\{ -\frac{||x - \eta||^2}{\lambda} \right\},\label{eqn:rbf}
\end{align}
where the width variable $\lambda$ is a parameter of the algorithm
(which may in principle be set according to location-specific tissue
conductance profiles) that governs the level of spatial smoothing.  In
choosing $\lambda$ for the analyses presented here, we sought to
maximize spatial resolution (which implies a small value of $\lambda$)
while also maximizing the algorithm's ability to generalize to any
location throughout the brain, including those without dense electrode
coverage (which implies a large value of $\lambda$). Using our prior
work as a guide~\citep{MannEtal14b, MannEtal18}, we set $\lambda = 20$,
although this could in theory be optimized, e.g., using cross
validation or a formal model~\citep[e.g.,][]{MannEtal18}.

@@

To illustrate our approach, we first examine and individual held-out
raw LFP trace and its associated SuperEEG-derived reconstruction.
Figure~\ref{fig:recon}A displays the observed LFP from the red
electrode in Figure~\ref{fig:methods}A (red), and its associated
reconstruction (blue), during a 5~s time window during one of the
example patient's six recording sessions.  The two traces match
closely ($r = XXX, p = XXX$).
%Where the traces do not align, the predicted
%trace tends to be rounded towards zero, reflecting the zero-mean prior
%implicit in Equation~\ref{eqn:reconstruction} (paired $t$-test
%comparing absolute values of actual versus predicted voltages:
%$t(XXX) = XXX, p = XXX$).
Figure~\ref{fig:recon}B displays a
two-dimensional histogram of the actual versus reconstructed voltages
for the entire 14.2 total hours of recordings from the example electrode
(correlation: $r = XXX, p = XXX$).
%Like in the shorter example trace
%shown in panel A, the reconstructed voltages throughout the full
%recording tended to be smaller in magnitude than the original
%recording ($t(XXX) = XXX, p = XXX$).
This example confirms that the SuperEEG algorithm recovers the
recordings from this single electrode well.  Next, we used this
general approach to quantify the algorithm's performance across the
full dataset.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information score by
      voxel.}  This panel is in the same format as Panel A.
    \textbf{C. Correspondence in information scores by voxel across
      Datasets 1 and 2.}  Same format as Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

>>>>

\newcommand{\perexpcorrmaps}{S1}
\newcommand{\perexptaskrecon}{S2}
\newcommand{\perexptaskreconseparated}{S3}
\newcommand{\suppstats}{S4}

@@

The recording from a given electrode is maximally informative about
the activity of the neural tissue immediately surrounding its
recording surface.  However, brain regions that are distant from the
recording surface of the electrode also contribute to the recording,
albeit (ceteris paribus) to a much lesser extent.  One mechanism
underlying these contributions is volume conduction.  The precise rate
of falloff due to volume conduction (i.e., how much a small volume of
brain tissue at location $x$ contributes to the recording from an
electrode at location $\eta$) depends on the size of the recording
surface, the electrode's impedance, and the conductance profile of the
volume of brain between $x$ and $\eta$.  As an approximation of this
intuition, we place a Gaussian radial basis function (RBF) at the
location $\eta$ of each electrode's recording surface
(Fig.~\ref{fig:methods}B).  We use the values of the RBF at any brain
location $x$ as a rough estimate of how much structures around $x$
contributed to the recording from location $\eta$:
\begin{align}
  \mathrm{rbf}(x|\eta,\lambda) & =
  \mathrm{exp}\left\{ -\frac{||x - \eta||^2}{\lambda} \right\},\label{eqn:rbf}
\end{align}
where the width variable $\lambda$ is a parameter of the algorithm
(which may in principle be set according to location-specific tissue
conductance profiles) that governs the level of spatial smoothing.  In
choosing $\lambda$ for the analyses presented here, we sought to
maximize spatial resolution (which implies a small value of $\lambda$)
while also maximizing the algorithm's ability to generalize to any
location throughout the brain, including those without dense electrode
coverage (which implies a large value of $\lambda$).  Here we set
$\lambda = 20$, guided in part by our prior work~\citep{MannEtal14b,
  MannEtal18}, and in part by examining the brain coverage with
non-zero weights achieved by placing RBFs at each electrode location
in Dataset 1 and taking the sum (across all electrodes) at each voxel
in a 4~mm$^3$ MNI brain.  (We then held $\lambda$ fixed for our
analyses of Dataset 2.)  We note that this value could in theory be
further optimized, e.g., using cross validation or a formal
model~\citep[e.g.,][]{MannEtal18}.

@@

To illustrate our approach, we first examine and individual held-out
raw LFP trace and its associated SuperEEG-derived reconstruction.
Figure~\ref{fig:recon}A displays the observed LFP from the red
electrode in Figure~\ref{fig:methods}A (red), and its associated
reconstruction (blue), during a 5~s time window during one of the
example patient's six recording sessions.  The two traces match
closely ($r = XXX, p = XXX$).  Figure~\ref{fig:recon}B displays a
two-dimensional histogram of the actual versus reconstructed voltages
for the entire 14.2 total hours of recordings from the example
electrode (correlation: $r = XXX, p = XXX$).  This example confirms
that the SuperEEG algorithm recovers the recordings from this single
electrode well.  Next, we used this general approach to quantify the
algorithm's performance across the full dataset.

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In Panels A and B the contours indicate the intersections between
    the top 10\% most informative voxels in each map.
    \textbf{C. Correspondence in information scores by voxel across
      Datasets 1 and 2.}  Same format as Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}
